BSOS

### 2014-06-05 Paper.tex
Update Paper.tex
Added Memory Management Introduction
TODO: Paragraph on theory, implementation, results and improvement potentials

\begin{lstlisting}
Pawe's stuff goes here.
\end{lstlisting}

>>>>

\begin{lstlisting}
\paragraph{Introduction}
In all modern computer systems arrises the necessesity to manage resources, in particular memory. Because a typical general purpose computer
may have many different programs running simulatneously it is crucial to have a subsystem that assigns memory regions to applications and keeps
track of those regions. In the case of modern operating systems the implementation of such a system may be done so based on different principles.
In a very simple Operating System which is responsible for managing resources for a small pool of applications the choice of paradigm does not have a large impact on system stability or performance.
With simpliciy taken into account, the BSOS memory management system assigns variable sized blocks of memory to applications and keeps track of their status.
\end{lstlisting}
